---
format: gfm
execute:
  echo: true   # show code
  warning: false
  message: false
---


# FPL data for season 2025-26 

## About

2025-08-22: Here I share data on the FPL 2025/26 season. So far I have not found a solution to get data on all 10 000 000 players.  Instead I am collecting data on 100 000 randomly selected players.  Please let me know if you find mistakes or something is missing. 

## Datasets

 1. fplplayer_ids.csv
 
    - content: list of fpl player included in the sample
    - generated by: data_get_fplplayer_ids.R 
    
 2. fpl_teams.parquet
 
    - content: team selections by gameweek
    - generated by: data_get_fpl_teams.R 
    
 3. fplplayer_entry_season.parquet
 
    - content: points (and points on bench) and rank by gameweek
    - generated by: data_get_fplplayer_info.R
 
 4. fplplayer_favourite_teams.parquet
  
    - content: favourite teams (numeric code)
    - generated by: data_get_fplplayer_info.R
    
 5. fplplayer_history.parquet

    - content: past performance
    - generated by: data_get_fplplayer_info.R
    
 6. fplplayer_mini_leauges.parquet
   
    - content: mini leagues 
    - generated by: data_get_fplplayer_info.R
    
 7. players.parquet

    - content: Premier League player prices, popularity, performance
    - generated by: data_get_players.R and data_join_players.R
  



## Examples

### Ownership 

```{r}
# Libraries
library("ggplot2")
# Load data 
df_players<-arrow::read_parquet("/Users/hhs/Dropbox/Bucket/fpl2526/data/players.parquet")

# Create chart
ggplot(df_players[df_players$web_name%in%c("Semenyo","Ekitiké","Gyökeres"),],  
      aes(x=time,y=selected_by_percent))+
    facet_wrap(~web_name)+
    geom_line()

```


### FPL player with id 6708968

#### League history

```{r}
# Load data 
df_history<-arrow::read_parquet("/Users/hhs/Dropbox/Bucket/fpl2526/data/fplplayer_history.parquet")

# Check data
df_history[df_history$fplid==6708968,]
```

#### Mini leagues
```{r}
# Load data 
df_leagues<-arrow::read_parquet("/Users/hhs/Dropbox/Bucket/fpl2526/data/fplplayer_leagues.parquet")

# Check data
df_leagues[df_leagues$fplid==6708968,]
```

#### Team selection

```{r}
# Load data 
df_teams<-arrow::read_parquet("/Users/hhs/Dropbox/Bucket/fpl2526/data/fplplayer_teams.parquet")

# Check data
df_teams[df_teams$fpl_entry_id==6708968,]
```

#### Points

```{r}
# Load data 
df_points<-arrow::read_parquet("/Users/hhs/Dropbox/Bucket/fpl2526/data/fplplayer_points.parquet")

# Check data
df_points[df_points$fplid==6708968,]
```



